% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2008 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.


\documentclass[a4paper]{article}


\usepackage{hyperref}
\usepackage{geometry}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[osf]{mathpazo}

\usepackage[danish]{babel}

\usepackage{lastpage}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% \chead[Curriculum Vitae for Anders Lemke]{Curriculum Vitae for Anders Lemke}
\cfoot{\thepage\ af \pageref{LastPage}}

\hypersetup{
  colorlinks,
  urlcolor = black,
  pdfauthor={Anders Lemke},
  pdfkeywords={},
  pdftitle={Curriculum Vitae},
  pdfsubject={Curriculum Vitae},
  pdfpagemode=UseNone
}

\geometry{textheight=9in, textwidth=6in}

% Customize section headings
\usepackage{sectsty}
\sectionfont{\sffamily}
% \subsectionfont{\rmfamily\mdseries\large}
% \subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}

% \usepackage{titlesec}
% \titleformat{\section}{\large\sffamily}{\thesection}{1em}{\hrule}

\newcommand{\keywords}[1]{\small\textbf{Keywords:} \emph{#1}\normalsize} 

% Don't indent paragraphs.
\setlength\parindent{0em}
\setlength\parskip{0.5em}

% Make lists without bullets
% \renewenvironment{itemize}{
%   \begin{list}{}
%     { \setlength{\itemsep}{5pt}
%       \setlength{\parsep}{0pt}
%       \setlength{\topsep}{0pt}
%       \setlength{\leftmargin}{0em} } }{
%   \end{list}}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

\begin{document}


{\huge\bf Anders Lemke}

\bigskip
Præstegårds Allé 50 \\
2700 Brønshøj \\
Denmark

\medskip

Mobile: +45 20442127

\medskip

Email: \href{mailto:mail@anderslemke.dk}{\tt mail@anderslemke.dk} \\
URL: \href{http://www.anderslemke.dk}{\tt http://www.anderslemke.dk} \\
Google+: \href{https://profiles.google.com/116409421545259976121}{\tt https://profiles.google.com/116409421545259976121} \\
GitHub: \href{http://www.github.com/anderslemke}{\tt http://www.github.com/anderslemke} \\
LinkedIn: \href{http://www.linkedin.com/in/anderslemke}{\tt http://www.linkedin.com/in/anderslemke} \\
Twitter: \href{http://www.twitter.com/anderslemke}{\tt http://www.twitter.com/anderslemke} 

\section*{Education}
Civil engineer in informatics, Technical University of Denmark, august 2008.

\section*{Experience}

\subsection*{Developer - Firmafon - 2013}
\keywords{Angular.js, Cordova, Ruby on Rails, Freeswitch, Puppet, RabbitMQ}

One of three developers, with main responsibility for our apps. Both in browser and on mobile.

Built our internal sales settling tool.

\subsection*{Senior Developer - Issuu - 2012-2013}
\keywords{Javascript, Ruby on Rails, node.js, SASS, Grunt}

Lead developer on \href{http://www.magmahq.com}{Magma} which is written in Ruby on Rails.

Works on issuu.com frontend, where I'm responsinble for certain areas.

\subsection*{autobutler.dk - 2011-2012}
\keywords{Project management, Ruby on Rails, Heroku}

In order to keep their product evolving Autobutler hired me to take care of the development.

\begin{itemize}
	\item General analysis, design and implementation in \emph{Ruby on Rails}.
\end{itemize}

\subsection*{Benjamin Media - 2009-2010}

\keywords{FreeBSD, Ruby on Rails, Capistrano, Unicorn, PostgreSQL, server architecture, creditcard payment, security}

At Benjamin Media, besides implementing features on our applications, my responsibility was to make our applications scale and keep them running smoothly.

\begin{itemize}
	\item Analyzed our application, pinpointed and solved bottlenecks.
	\item Did a major restructuring of our servers switching from Mongrel to Unicorn.
	\item Implemented credit card payment on our subscription signups.
\end{itemize}

\subsection*{Gigahost ApS - 2008}

\keywords{Linux, PHP, webudvikling, Apache, MySQL, serveradministration, selvstændigt, Mogile FS}

\begin{itemize}
	\item Configured the distributed file system Mogile FS to be used for images on speek.dk among other things.
	\item Implemented a domain renewal system for Gigahost customers to use to manage their domains.
	\item Configured PowerDNS and an administration system around it.
\end{itemize}

\section*{Other projects}

\subsection*{Syncing Tasks - 2011}
\keywords{iPhone/iOS app development, Objective-C, Ruby on Rails, Google Web Toolkit (GWT), Unicorn, nginx}

I wanted a task manager that synced to my iPhone like my mail and calendar did (using Google Sync).

\begin{itemize}
\item Implemented an iPhone application using \emph{Objective-C}.
\item Implemented a web application using \emph{Ruby on Rails} and \emph{Google Web Toolkit}.
\item Configured a server to run the application using \emph{nginx} and \emph{Unicorn}.
\item Designed and implemented the marketing site at \href{http://www.syncingtasks.com}{www.syncingtasks.com}.
\end{itemize}

You can read more about Syncing Tasks at \href{http://www.syncingtasks.com}{www.syncingtasks.com}.
\subsection*{hurtigfaktura.dk - 2008}
\keywords{Ruby on Rails, HAML, \LaTeX}

I needed a quick and easy way to generate an invoice, so I created hurtigfaktura.dk to do just that.

\begin{itemize}
	\item Implemented a small application in Ruby on Rails running on hurtigfaktura.dk.
	\item Setup \LaTeX on a Linux server to generate the invoices.
\end{itemize}

\subsection*{Image archive for Personalestyrelsen - 2007} 
\keywords{Ajax, Java, GUI}
Personalestyrelsen needed a system to keep track of images bought for publications.

\begin{itemize}
	\item Implemented an application using ASP as backend and Google Web Toolkit as frontend.
\end{itemize}

\section*{Competencies}

\begin{itemize}
\item \textbf{Languages}: Ruby, Objective-C, JavaScript.
\item \textbf{OS}: Mac OS X, Linux, Unix.
\item \textbf{Databases}: MySQL, SQLite, MSSQL, MongoDB.
\item \textbf{Other}: Ruby on Rails, testing, \LaTeX, configuration of Apache, DNS, HTML, CSS, RSpec, Subversion, Git.
\end{itemize}


\section*{I love}

\begin{itemize}
  \item \textbf{Software development}, being \emph{my} tool to make the world a better place.
  \item \textbf{Beautiful, simple and user friendly design}, being the way to make the world an easier and more aestheticly  pleasing place to be.
  \item \textbf{Ruby on Rails}, being a simple framework, that allows me to create good products easily.
  \item \textbf{Innovation}, being the process of identifying needs and proposing creative solutions.
\end{itemize}


\section*{Personal}
Born december 12th, 1980.

I \textbf{am} positive, calm, ambitious, engaged.

I \textbf{love} quality, simplicity, transparency, innovation, good design.

\section*{Personal interests} 

Music, sport (running, swimming, mountainbiking), philosphy, travelling.


\bigskip

% Footer
\begin{center}
\begin{footnotesize}
Last updated: \today \\
\href{http://files.anderslemke.dk/cv.en.pdf}{\tt http://files.anderslemke.dk/cv.en.pdf}
\end{footnotesize}
\end{center}
\end{document}
