%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template: Curriculum Vitae
%
% Source: http://www.howtotex.com/
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: July 2011
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
                            
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{changepage}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
    \textheight=700px                    % Saving trees ;-)
\usepackage{url}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\lfoot{Curriculum Vitae}
\cfoot{\thepage\ / \pageref{LastPage}}
\rfoot{Anders Lemke-Holstein}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\setlength{\parindent}{0em}
\setlength{\parskip}{0.4em}

\sectionfont{%                        % Change font of \section command
    \usefont{OT1}{phv}{b}{n}%        % bch-b-n: CharterBT-Bold font
    \sectionrule{0pt}{0pt}{-5pt}{0.1pt}}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}            % Box to align text
\newcommand{\sepspace}{\vspace*{1em}}        % Vertical space macro

\renewcommand*\baselinestretch{1.1}\selectfont

\newcommand{\MyName}[1]{ % Name
  \begin{center}
    \Huge \usefont{OT1}{phv}{b}{n} #1
    \par \normalsize \normalfont
  \end{center}
  }

\newcommand{\MySlogan}[1]{ % Slogan (optional)
  \begin{center}
    \large \usefont{OT1}{phv}{m}{n} \textit{#1}
        \par \normalsize \normalfont
        \end{center}
        }

\newcommand{\NewPart}[1]{\section*{#1}}

\newcommand{\PersonalEntry}[2]{
        \noindent % Indentation
        \parbox{\spacebox}{        % Box to align text
        #1}               % Entry name (birth, address, etc.)
        \hspace{1.5em} #2 \par}    % Entry value

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
        \noindent\hangindent=2em\hangafter=0 % Indentation
        \parbox{\spacebox}{        % Box to align text
        \textit{#1}}               % Entry name (birth, address, etc.)
        \hspace{1.5em} #2 \par}    % Entry value    
        
\newcommand{\EducationEntry}[4]{
        \noindent \textbf{#1} \hfill      % Study
        \colorbox{Black}{%
            \parbox{6em}{%
            \hfill\color{White}#2}} \par  % Duration
        \noindent \textit{#3} \par        % School
        \begin{adjustwidth}{2.0em}{3em}
#4
        \end{adjustwidth}
        \sepspace
        \normalsize \par}


%%% Begin Document
%%% ------------------------------------------------------------
\begin{document}
{\fontfamily{qhv}\selectfont

\MyName{Anders Lemke-Holstein}
\MySlogan{Human centered software engineer}

%%% Profile
%%% ------------------------------------------------------------
\NewPart{Profile}{}
Hi, I'm Anders. A sotware engineer with a focus on ethics and compassion.

Interacting with software should be a positive experience. Both for users and engineers. At the same time, (most) software has to fulfill a business objective. These two areas of interst are not mutually exclusive. This is why I make an effort to find the balance between business value and human delight when building software.

I'm genuinely motivated by making people around me feel content, safe and welcome.

%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}

\EducationEntry{Master of Science in Engineering (cand.polyt)}{2003-2008}{Technical University of Denmark (DTU)}{Studied Informatics (the combination of computer science and applied mathematics) and had an introductory management course.}

%%% Work experience
%%% ------------------------------------------------------------
\NewPart{Experience}{}

\EducationEntry{Platform Architect and Lead Engineer}{2015-present}{Zetland}{
  Built a platform using modern software engineering best practices in close collaboration with the product team. The platform is used to distribute and consume high quality journalistic content.
  
  Acquired deep working knowledge of event-based architectures in a microservice-like environment.

  Worked extensively with frontend technologies like React, Node.js and GraphQL (both server and client).

  Applied concepts from Domain-Driven Design successfully.

  Took part in recruiting, coaching, mentoring and teaching both junior and senior developers.
}

\EducationEntry{Senior Developer}{2013-2015}{Firmafon}{
  Got my first experience with distributed real-time event-based systems.

  Experienced the importance of an ubiquitious language and how it influences the business and developer happiness.

  Part of recruiting to the team.
}

\EducationEntry{Senior Developer}{2012-2013}{Issuu}{
  Became aware that build tools and operations has a big impact on both developer experience and product velocity.
}

\EducationEntry{CTO}{2011-2012}{Autobutler}{
  Gained experience with TDD and realized how important automated tests are both for product quality and programmer happiness.

  First experience with recruiting and leading a team.
}

\EducationEntry{Developer}{2009-2010}{Benjamin Media}{
  Experience with scaling and maintaining some of the most visited sites in Denmark. Inluding msn.dk.
}

\EducationEntry{Developer}{2008}{Gigahost}{
  Got a deep practical understanding of the internet infrastructure.
}

\NewPart{Talks}{}

\EducationEntry{Just authentication for the internet}{2020}{PasswordsCon (a track on Internetdagarna)}{
  An introduction to my utopian side-project, Promise, that proposes how we might solve authentication in a simple yet secure way.
}

\EducationEntry{The physiological aspects of ambiguity}{2019}{Copenhagen Ruby Brigade}{
  A talk about what happens in our bodies and brains when we're faced with ambiguity. And it's not pleasant. Being a software developer potentially puts you in a lot of ambigous situations, so I pull in aspect from linguistics to help us understand how to avoid ambiguity in the first place.
}

\EducationEntry{Applied Event Sourcing, Domain Driven Design and CQRS}{2018}{Copenhagen Ruby Brigade}{
  A talk where I explain the basics of the concepts of Event Sourcing, some concepts from Domain-Driven Design and CQRS and how they are applied in the platform of Zetland.
}

%%% Personal details
%%% ------------------------------------------------------------
\NewPart{Personal details}{}

\PersonalEntry{Born}{December 12, 1980}
\PersonalEntry{Address}{Præstegårds Allé 50, 2700 Brønshøj}
\PersonalEntry{Phone}{+45 20442127}
\PersonalEntry{Mail}{anders@lemke.dk}
\PersonalEntry{LinkedIn}{linkedin.com/in/anderslemke}
\PersonalEntry{GitHub}{github.com/anderslemke}
\PersonalEntry{Weekends}{Spent with my family and on my bike.}

%%% Personal details
%%% ------------------------------------------------------------
% \NewPart{Other}{}
} % font selection
\end{document}
